Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-25 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed the paths for saving the figures
Revised the general analyses paragraph

if (!dir.exists(here::here(figs_dir))) {
  dir.create(here::here(figs_dir),
    showWarnings = TRUE
  )
}
```

@@

## Number of studied included
Number of studies included `r nrow(compact_data_with_citation_keys)` in review.

>>>>

if (!dir.exists(here::here(gh_figs_dir))) {
  dir.create(here::here(gh_figs_dir),
    showWarnings = TRUE
  )
}
```

@@

## Number of studies included

The review involved `r nrow(compact_data_with_citation_keys)` published between
`r min(compact_data_with_citation_keys$publication_year)` and `r max(compact_data_with_citation_keys$publication_year)`.
